Software Citation Principles

### 2016-02-14 sc-principles/software-citation-principles.tex
cleaned up use cases section a bit

\usepackage{color}
\usepackage{dcolumn}
\usepackage{float}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{subfigure}
\usepackage{psfrag}
\usepackage{tabularx}
\usepackage[hyphens]{url}
\usepackage{wrapfig}
\usepackage{longtable}
\usepackage{verbatim}
\usepackage{booktabs,multicol}

@@

\newcommand{\katznote}[1]{ {\textcolor{blue} { ***DSK: #1 }}}
\newcommand{\niemeyernote}[1]{ {\textcolor{orange} { ***KEN: #1 }}}

@@

We have documented and analyzed a set of use cases related to software citation in \cite{SC-Use-Cases}.  Table~\ref{tab:use_cases} summarizes these use cases and makes clear what the requirements are for software citation in each case.  \katznote{not sure if this next long sentence should be here, should be in the table caption, or should be footnotes to the table, or even more than one of these} In the table, 
``researcher'' includes academic researchers (e.g., postdoc, tenure-track faculty member) and research software engineers
``publisher'' includes both traditional publishers that publish text and\slash or software papers as well as archives such as Zenodo that directly publish software; ``reproduce'' can mean reproduction, replication, verification, validation, repeatability, and\slash or utility; 
examples of indexers include Scopus, Web of Science, Google Scholar, and Microsoft Academic Search;  
domain groups include ASCL, bioCADDIE, CIG, etc.;
``repository'' is ???; and
``funder'' is a group that funds software or work using software.

\begin{table}[htbp]
\caption{Use cases for software citation, adapted from \cite{SC-Use-Cases}}
\katznote{I changed DOI to UID, meaning unique ID - I think we probably want to be general here}
\centering
\scriptsize\setlength{\tabcolsep}{2.5pt}
\begin{tabular}{@{}l l c c c c c c c c@{}}
\toprule
 & & \multicolumn{6}{c}{Requirements} \\
 \cmidrule{3-10}
\multirow{2}{*}{Stakeholder} &	\multirow{2}{*}{Use\slash wants to} 	 &  Software  & \multirow{2}{*}{Author(s)} & \multirow{2}{*}{Version \#} & Release & Location\slash  & \multirow{2}{*}{UID} & Indexed & \multirow{2}{*}{Role} \\
& & name &  &  &  date & repository &  & citations & \\
\midrule
Researcher & someone else's software for a paper	& \textbullet	& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & & \\
Researcher & someone else's software for new software& \textbullet	& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & & \\
Researcher & contribute to software 				& \textbullet	& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & & \textbullet \\
Researcher & find citations of software 			& \textbullet &   &   &   &   & \textbullet & \textbullet & \\
Researcher & credit for software development		& \textbullet & \textbullet &   & \textbullet & \textbullet & \textbullet & & \textbullet \\
Researcher & ``reproduce'' analysis 				& \textbullet &   & \textbullet & \textbullet & \textbullet & \textbullet & & \\
Researcher & benchmark software 					& \textbullet &   & \textbullet & \textbullet & \textbullet & \textbullet & & \\
Researcher & find software to implement task 		& \textbullet & \textbullet &   &   & \textbullet & \textbullet & \textbullet & \\
Publisher & publish software paper					& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & & \\
Publisher & publish papers that cite software 		& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \\
Indexer & build catalog of software 				& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \\
Domain group & build catalog of software 			& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &  & \\
Library\slash archive & build catalog of software 	& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &  & \\
Repository & show scientific impact of holdings 	& \textbullet &   &   &   &   & \textbullet & \textbullet & \\
Funder & show how funded software has been used		& \textbullet &   &   &   &   & \textbullet & \textbullet & \\
\bottomrule
\end{tabular}
\label{tab:use_cases}
\end{table}%

Alternate metadata
\begin{itemize}
\item version number and release date: download date
\item location\slash respository: contact name\slash email if not publicly available
\end{itemize}

>>>>

\usepackage{xcolor}
\usepackage{dcolumn}
\usepackage{float}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{subfigure}
\usepackage{psfrag}
\usepackage{tabularx}
\usepackage[hyphens]{url}
\usepackage{wrapfig}
\usepackage{longtable}
\usepackage{verbatim}
\usepackage{booktabs,multicol}

@@

\newcommand{\katznote}[1]{ {\textcolor{blue} { ***DSK: #1 }}}
\newcommand{\niemnote}[1]{ {\textcolor{orange} { ***KEN: #1 }}}

@@

We have documented and analyzed a set of use cases related to software citation in \cite{SC-Use-Cases}. 
Table~\ref{tab:use_cases} summarizes these use cases and makes clear what the requirements are for software citation in each case. 
\katznote{not sure if this next long sentence should be here, should be in the table caption, or should be footnotes to the table, or even more than one of these}
\niemnote{Not sure either; definitely should include in the text due to length. Maybe an abbreviated version in the caption?}
In the table,
``researcher'' includes both academic researchers (e.g., postdoc, tenure-track faculty member) and research software engineers;
``publisher'' includes both traditional publishers that publish text and\slash or software papers as well as archives such as Zenodo that directly publish software;
``reproduce'' can mean reproduction, replication, verification, validation, repeatability, and\slash or utility;
examples of indexers include Scopus, Web of Science, Google Scholar, and Microsoft Academic Search; 
domain groups include bioCADDIE, CIG, etc.;
``repository'' refers to open-source software repositories such as ASCL, GitHub, Netlib, CRAN, institutional repositories; 
``funder'' is a group that funds software or work using software; and 
``UID'' means unique ID, such as DOI or PURL.

\begin{table}[htbp]
\caption{Use cases for software citation, adapted from \cite{SC-Use-Cases}}
\centering
\scriptsize\setlength{\tabcolsep}{2.5pt}
\begin{tabular}{@{}l l c c c c c c c c@{}}
\toprule
 & & \multicolumn{6}{c}{Requirements} \\
 \cmidrule{3-10}
\multirow{2}{*}{Stakeholder} &	\multirow{2}{*}{Use\slash wants to} 	 &  Software  & \multirow{2}{*}{Author(s)} & \multirow{2}{*}{Version \#} & Release & Location\slash  & \multirow{2}{*}{UID} & Indexed & \multirow{2}{*}{Role} \\
& & name &  &  &  date & repository &  & citations & \\
\midrule
Researcher & someone else's software for a paper	& \textbullet	& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & & \\
Researcher & someone else's software for new software& \textbullet	& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & & \\
Researcher & contribute to software 				& \textbullet	& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & & \textbullet \\
Researcher & find citations of software 			& \textbullet &   &   &   &   & \textbullet & \textbullet & \\
Researcher & credit for software development		& \textbullet & \textbullet &   & \textbullet & \textbullet & \textbullet & & \textbullet \\
Researcher & ``reproduce'' analysis 				& \textbullet &   & \textbullet & \textbullet & \textbullet & \textbullet & & \\
Researcher & benchmark software 					& \textbullet &   & \textbullet & \textbullet & \textbullet & \textbullet & & \\
Researcher & find software to implement task 		& \textbullet & \textbullet &   &   & \textbullet & \textbullet & \textbullet & \\
Publisher & publish software paper					& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & & \\
Publisher & publish papers that cite software 		& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \\
Indexer & build catalog of software 				& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \\
Domain group & build catalog of software 			& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &  & \\
Library\slash archive & build catalog of software 	& \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &  & \\
Repository & show scientific impact of holdings 	& \textbullet &   &   &   &   & \textbullet & \textbullet & \\
Funder & show how funded software has been used		& \textbullet &   &   &   &   & \textbullet & \textbullet & \\
\bottomrule
\end{tabular}
\label{tab:use_cases}
\end{table}%

If certain metadata are not available, alternates may be provided:
\begin{itemize}
\item version number and release date: download date
\item location\slash respository: contact name\slash email if not publicly available
\end{itemize}
